Gafo-cc-analysis

### 2024-01-19 analysis/gafo-cc-analysis.Rmd
prep model run in cluster

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  ungroup()%>%
  mutate(older_children = children - 1 - younger_children)%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         touchscreen = factor(touchscreen),
        screen = factor(screen),
        click = abs(clickdistfromtargetcenterx))%>%
  group_by(community)%>%
  mutate(children = scale(children),
         household = scale(household),
         younger_children = scale(younger_children),
         older_children = scale(older_children))%>%
  select(subjid,community,ageinyears,children, household, younger_children,older_children, trialnr, screen,touchscreen, targetcentralityx, click )

@@

fixef(bm_octs_rand)
```
```{r}
ndata <- scdata%>%
  distinct(community, ageinyears)

@@

```{r}
bm_trial_base <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))
```

@@

bm_base <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

@@

bm_cult_x_age <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (ageinyears |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

>>>>

```{r}
exclude <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  filter(children == younger_children, trialnr == 1)%>%
  pull(subjid)

mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  ungroup()%>%
  filter(!subjid %in% exclude)%>%
  mutate(older_children = children - 1 - younger_children)%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         touchscreen = factor(touchscreen),
        screen = factor(screen),
        click = abs(clickdistfromtargetcenterx))%>%
  group_by(community)%>%
  mutate(children = scale(children),
         household = scale(household),
         younger_children = scale(younger_children),
         older_children = scale(older_children))%>%
  select(subjid,community,ageinyears,children, household, younger_children,older_children, trialnr, screen,touchscreen, targetcentralityx, click )

@@

fixef(bm_octs_fix)
```
```{r}
ndata <- scdata%>%
  distinct(community, ageinyears)

@@

```{r}
bm_trial_base <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata%>%na.omit(), 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

saveRDS(bm_trial_base, "../saves/bm_trial_base.rds")

bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children + targetcentralityx |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

saveRDS(bm_trial_pred, "../saves/bm_trial_pred.rds")

loo_compare(bm_trial_base,
            bm_trial_pred
            )%>%as_tibble(rownames = "model")

fixef(bm_trial_pred)
```

```{r}
draws <- bind_rows(
as_draws_df(bm_trial_pred)%>%
  select(contains("children"))%>%
  select(contains("children"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  pivot_longer(cols = contains("children]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_older_children, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",older_children]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "older_children"),

as_draws_df(bm_trial_pred)%>%
  select(contains("touchscreen"))%>%
  select(contains("touchscreen"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  pivot_longer(cols = contains("touchscreen1]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_touchscreen1, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",touchscreen1]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "touchscreen"),

as_draws_df(bm_trial_pred)%>%
  select(contains("ageinyears"))%>%
  select(contains("ageinyears"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_ageinyears, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",ageinyears]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "ageinyears"),

as_draws_df(bm_trial_pred)%>%
  select(contains("targetcentralityx"))%>%
  select(contains("targetcentralityx"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  select(-contains("subjid"))%>%
  pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_targetcentralityx, 
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",targetcentralityx]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "targetcentrality")

)

pdraws <- draws%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Sambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Turkey)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "Bayaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))

saveRDS(pdraws, "../saves/pdraws.rds")

pdraws <- readRDS("../saves/pdraws.rds")

ggplot(pdraws, aes(x= post, y = community))+
  #geom_density_ridges(rel_min_height = 0.005, col = "black", alpha = .75, fill = NA)+
  geom_density_ridges(rel_min_height = 0.005, col = "white", alpha = .75, fill = "grey")+
  geom_vline(xintercept = 0, lty = 3)+
  facet_grid(continent~type, scales = "free", space = "free_y")+
  #stat_pointinterval(size = 0.1)+
  #xlim(-0.15, 0.1)+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "black", fill=NA, size = .5))

@@

bm_null <- brm(click ~ targetcentralityx + (trialnr + targetcentralityx|subjid),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

@@

bm_cult_x_age <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")
